### 2023-09-14 3.Design/crossbar.tex
new figures and few lines

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{crossbar/crossbarUse}
  \caption{Simplified circuit of a crossbar array ($n_i$, $n_o$, $n_s$)}
  \label{circt:xbar}
\end{figure}

@@

This design is the one that is used in \cite{doubleMem}. Let's assume that a given memristor has a resistance range of $R\in[R_{min},R_{max}]$, that means it's conductance range is $\sigma \in [\sigma_{min},\sigma_{max}]$ (with $\sigma_{min}= \frac{1}{R_{max}}$ and $\sigma_{max}= \frac{1}{R_{min}}$). This design works using two \ac{opAmp} connected to $V_{cm}$ with the positive pin and the negative pin to the output of the crossbar array. \Cref{eq:doubleMem0,eq:doubleMem1,eq:doubleMem2} are describing how this architecture works.

% For the sake of simplicity, the following equations considers the ground to be $V_{cm}$.

\begin{equation}
  \label{eq:doubleMem0}
  V_{opAmp0}=-R\cdot i_+ \Leftrightarrow
\end{equation}
\begin{equation}
  \label{eq:doubleMem1}
  i_{R_f}=i_-+\frac{V_{opAmp0}}{R}=i_--i_+
\end{equation}
With $i_{opAmp}=0A$ because we assume an ideal \ac{opamp}.
\begin{equation}
  \label{eq:doubleMem2}
  V_{opAmp2}=V_{out}=-R_f\cdot(i_--i_+)=R_f\cdot(i_+-i_-)=R_f\cdot\sum_{k=0}^n(\sigma_{k+}-\sigma_{k-})\cdot x_k
\end{equation}
With $i_+=\sum_{k=0}^n\sigma_{k+}\cdot x_k$ and $i_-=\sum_{k=0}^n\sigma_{k-}\cdot x_k$.

In \cref{eq:doubleMem0,eq:doubleMem1,eq:doubleMem2}, $x_k$ is the voltage for the input line $k$.

@@

\begin{figure}[H]
  \centering
  \begin{tikztimingtable}%TODO change or find other way
    Input data & x6D{$x_1$}6D{$x_2$}6D{$x_3$}x \\
    Input enable & xL2H2L3H7L2HLx\\
    Output enable & x3L2H4L5H1L3Hx\\
    Memory & xU4D{$x_1$}10D{$x_2$}3D{$x_3$}x \\
    Output data & x3U2D{$x_1$}4U5D{$x_2$}U3D{$x_3$}x \\
    \extracode
    \tablerules
    %\draw (0,0) circle (2pt); % Origin
    \begin{pgfonlayer}{background}
      \vertlines[help lines]{0.6,18.6}
      %\vertlines[red]{1.6,5.6,15.6}
      %\vertlines[blue]{3.6,9.6,15.6}
    \end{pgfonlayer}
  \end{tikztimingtable}
  \caption{Time diagram that shows the states of the enable flags for the crossbar circuit}
  \label{tim:serpar}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth]{crossbar/crossbarUse}
  \caption{Circuit of the crossbar array used in the final system ($n_i$, $n_o$, $n_s$)}
  \label{circt:xbar}
\end{figure}

@@

This design is the one that is used in \cite{doubleMem}. Let's assume that a given memristor has a resistance range of $R\in[R_{min},R_{max}]$, that means it's conductance range is $\sigma \in [\sigma_{min},\sigma_{max}]$ (with $\sigma_{min}= \frac{1}{R_{max}}$ and $\sigma_{max}= \frac{1}{R_{min}}$). This design works using two \ac{opAmp} connected to $V_{cm}$ with the positive pin and the negative pin to the output of the crossbar array. \Cref{eq:doubleMem0,eq:doubleMem1,eq:doubleMem2} are describing how this architecture works. A simplified version of the double memristors per synapse circuit is also available in \cref{circt:doubleMem}.

\begin{figure}[H]
  \centering
  \includesvg[height=8cm]{crossbar/doubleMem}
  \caption{Simplified circuit of a double memristor per synapse architecture}
  \label{circt:doubleMem}
\end{figure}

With $x_k$ being the voltage for the input line $k$. The highest \ac{opAmp} is identified as opamp0 and the lowest opamp1.

For the sake of simplicity, the following equations considers the ground to be $V_{cm}$.

\begin{equation}
  \label{eq:doubleMem0}
  V_{opAmp0}=-R\cdot i_+ \Leftrightarrow
\end{equation}
\begin{equation}
  \label{eq:doubleMem1}
  i_{R_f}=i_-+\frac{V_{opAmp0}}{R}=i_--i_+
\end{equation}
With $i_{opAmp}=0A$ because we assume an ideal \ac{opamp}.
\begin{equation}
  \label{eq:doubleMem2}
  V_{opAmp2}=y_0=-R_f\cdot(i_--i_+)=R_f\cdot(i_+-i_-)=R_f\cdot\sum_{k=0}^n(\sigma_{k+}-\sigma_{k-})\cdot x_k
\end{equation}
With $i_+=\sum_{k=0}^n\sigma_{k+}\cdot x_k$ and $i_-=\sum_{k=0}^n\sigma_{k-}\cdot x_k$.

@@

The \ac{CMOS} switches are here to open the necessary input gates when the output is required, the gates are controlled as in \cref{tim:serpar}.
\begin{figure}[H]
  \centering
  \begin{tikztimingtable}%TODO change or find other way
    $e_0$ & xH3Lx\\
    $e_1$ & xLH2Lx\\
    $e_2$ & x2LHLx\\
    $e_3$ & x3LHx\\
    \extracode
    \tablerules
    %\draw (0,0) circle (2pt); % Origin
    \begin{pgfonlayer}{background}
      \vertlines[help lines]{0.6,4.6}
      %\vertlines[red]{1.6,5.6,15.6}
      %\vertlines[blue]{3.6,9.6,15.6}
    \end{pgfonlayer}
  \end{tikztimingtable}
  \caption{Example of enable flags timing with $n_s=4$ in a single time step}
  \label{tim:serpar}
\end{figure}
